Clicks and Cliques

### 2018-12-28 papersoul.Rnw
fig.height in econ chunck

### VARIFICAR NOMBRES REPETIDOS EN SVYVAR !!!!!!!

life <- soul.red2 %>% 
  filter(!is.na(PROJWT), prop.res <= 1) %>% 
  mutate(pr = PROJWT/3)  %>% 
  svydesign(ids =~1, strata =~QSB, weights =~pr, data = .) %>% 
  svyby(~prop.res + QD1 + CCE, ~QSB, 
               design = ., svymean, keep.var = TRUE, na.rm = T)

lifevar <- svyby(~prop.res + CCE, ~QSB, des.wt, svyvar, keep.var = TRUE, na.rm = T)
lifevar$rho <- with(lifevar, V2/sqrt(V1*V4))

@@

The bottom panel of Figure \ref{eco} presents the U.S. GDP growth rate in 2008, 2009, and 2010. A similar pattern is observed in both panels, suggesting the economic dimension is less related with attachment during the economic crisis.
\begin{figure}[hbpt]
<<econ, dependson=c('data'), echo=FALSE,message=FALSE,warning=FALSE, fig.height=5>>=
svydesign(ids =~ 1, strata =~ QSB, weights =~ PROJWT, data = filter(soul,!is.na(PROJWT))) %>% 
  svyby( ~ ECONOMY + CCE, ~ YEAR, design = ., svyvar, keep.var = TRUE, na.rm = T)  %>% data.frame() %>% select(1:5) %>% 
  mutate(rho = V2/sqrt(V1*V4), gdp = c(-0.4,-3.5,3.0)) %>% 
  gather(variable, value,rho,gdp) %>% 
  select(YEAR, variable, value) %>% 
  mutate(variable =  factor(variable, labels = c('GDP Rate','Attachment-Economy correlation'))) %>% ggplot(aes(x = YEAR, y = value)) + 
  geom_line() + geom_point() +
  labs(x = "", y = "", 
       title = 'Evolution of Attachment-Economy correlation and GDP') +
  facet_grid(facets = variable~., scales = 'free') + 
  ggtitle('Evolution of Attachment-Economy correlation and GDP')

>>>>

### VARIFICAR NOMBRES REPETIDOS EN SVYVAR !!!!!!!
life <- svyby(~prop.res + QD1 + CCE, ~QSB, des.wt, svymean, keep.var = TRUE, na.rm = T)
lifevar <- svyby(~prop.res + CCE, ~QSB, des.wt, svyvar, keep.var = TRUE, na.rm = T)
lifevar$rho <- with(lifevar, V2/sqrt(V1*V4))

@@

The bottom panel of Figure \ref{eco} presents the U.S. GDP growth rate in 2008, 2009, and 2010. A similar pattern is observed in both panels, suggesting the economic dimension is less related with attachment during the economic crisis.
\begin{figure}[hbpt]
<<econ, dependson=c('data'), echo=FALSE,message=FALSE,warning=FALSE, fig.height=4.7>>=
svydesign(ids =~ 1, strata =~ QSB, weights =~ PROJWT, data = filter(soul,!is.na(PROJWT))) %>% 
  svyby( ~ ECONOMY + CCE, ~ YEAR, design = ., svyvar, keep.var = TRUE, na.rm = T)  %>% data.frame() %>% select(1:5) %>% 
  mutate(rho = V2/sqrt(V1*V4), gdp = c(-0.4,-3.5,3.0)) %>% 
  gather(variable, value,rho,gdp) %>% 
  select(YEAR, variable, value) %>% 
  mutate(variable =  factor(variable, labels = c('GDP Rate','Attachment-Economy correlation'))) %>% ggplot(aes(x = YEAR, y = value)) + 
  geom_line() + geom_point() +
  labs(x = "", y = "", 
       title = 'Evolution of Attachment-Economy correlation and GDP') +
  facet_grid(facets = variable~., scales = 'free') + 
  ggtitle('Evolution of Attachment-Economy correlation and GDP')
